### 2019-04-22 Manuscript/Manuscript.tex
new checkpoint post-revisions

We use 15\textdegree~S to 15\textdegree~N as the definition of the tropical rain belt, as those latitudes approximately correspond with a sharp increase in zonal mean precipitation to values greater than 1.0~m/yr in modern climatalogical data \citep{Kalnay1996a}. Other parameters that could be used to define the tropical rain belt are runoff and evaporation minus precipitation (E--P). In modern climatological data, runoff sharply increases to values above 0.6~kg/m$^{2}$ between approximately 10 and 20\textdegree\xspace, and E--P sharply decreases to values below 1.5~kg/m$^{2}$/day between approximately 10 and 15\textdegree. Given that it is unclear as to which of these parameters correlates most strongly with long term weathering rates in natural environments, we also tested the sensitivity of our results to the assumed width of the tropical rain belt by performing the tropical LIP area calculations with tropical rain belt widths of $\pm$10\textdegree\xspace and $\pm$20\textdegree. Testing different tropical rain belt widths also has the indirect effect of accounting for uncertainties in the paleolatitude of LIPs in the paleogeographic model. We find that the $\pm$10\textdegree\xspace and $\pm$20\textdegree\xspace tropical rain belts yield similar results to that defined as $\pm$15\textdegree\xspace (Table \ref{tab:stats}).

@@

>>>>

We use 15\textdegree~S to 15\textdegree~N as the definition of the tropical rain belt, as those latitudes approximately correspond with a sharp increase in zonal mean precipitation to values greater than 1.0~m/yr in modern climatalogical data (\citealp{Kalnay1996a}; Fig. \ref{fig:Climatology}). Other parameters that could be used to define the tropical rain belt are runoff and evaporation minus precipitation (E--P). In modern climatological data, runoff sharply increases to values above 0.6~kg/m$^{2}$ between approximately $\pm$10\textdegree\xspace and $\pm$15\textdegree\xspace (\citealp{Kalnay1996a}; Fig. \ref{fig:Climatology}), and E--P sharply decreases to values below 1.5~kg/m$^{2}$/day also between approximately $\pm$10\textdegree\xspace and $\pm$15\textdegree\xspace (\citealp{Trenberth2011a}; Fig. \ref{fig:Climatology}). Given that it is unclear as to which of these parameters correlates most strongly with long term weathering rates in natural environments, we also tested the sensitivity of our results to the assumed width of the tropical rain belt by performing the tropical LIP area calculations with a tropical rain belt width of $\pm$10\textdegree\xspace. We also calculated the area of LIPs within $\pm$20\textdegree\xspace of the equator (a width that includes part of the arid subtropics) in order to account for uncertainties in the paleolatitude of LIPs in the paleogeographic model. We find that both of these additional analyses (LIP area calculated within $\pm$10\textdegree\xspace and $\pm$20\textdegree\xspace of the equator) yield similar results to that when LIP area is calculated within $\pm$15\textdegree\xspace of the equator (Table \ref{tab:stats}).

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{Manuscript/Figures/Climatology.pdf}
	\caption{Zonally averaged modern climatological data used to define the tropical rain belt. The global precipitation \citep{Kalnay1996a} and evaporation minus precipitation \citep{Trenberth2011a} data include land and ocean pixels, whereas global runoff and temperature \citep{Kalnay1996a} data are from land only. The peak in runoff $\sim$-50\textdegree\xspace is due to anomalously high runoff in the southern Andes, which represents almost all of the land in that latitude belt. Temperature data for Antarctica are off scale. Precipitation, runoff, and evaporation minus precipitation all increase/decrease sharply between $\pm$10\textdegree\xspace and $\pm$15\textdegree\xspace.}
	\label{fig:Climatology}
\end{center}
\end{figure}
